Efficient High-Level Abstractions for Web Programming

### 2013-11-04 papers/gpce2013/gpce19c-foy.tex
update paper

\documentclass[preprint]{sigplanconf}

@@

\input{macros}

@@

\conferenceinfo{GPCE '13}{October 27--28, 2013, Indianapolis, Indiana, USA} 
\copyrightyear{2013}
\copyrightdata{[to be supplied]}

@@

\terms Languages, Software Engineering

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=7.5cm]{langs.pdf}
\end{center}
\caption{Language engineering processes}
\vspace{-0.5cm}
\label{fig:langs}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=5cm]{ir.pdf}
\end{center}
\caption{Intermediate representations returned by the evaluation of (a)
\code{document.find("\#add-user button")} and (b) \code{document.find("\#add-user")}}
\label{fig:ir}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=8cm]{selectors-benchmark.png}
\caption{Micro-benchmark on the selectors abstraction}
\label{fig:selectors-benchmark}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=8cm]{microbenchmark.png}
\caption{Micro-benchmark on the optional values abstraction}
\label{micro-benchmark}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=8cm]{chooze.png}
\caption{Benchmarks on a real application}
\label{benchmark}
\end{figure}

@@

\bibliographystyle{abbrvnat}
\bibliography{biblio}
%\begin{thebibliography}{}
%\softraggedright
%
%\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
%P. Q. Smith, and X. Y. Jones. ...reference text...
%
%\end{thebibliography}
%
\end{document}

>>>>

\documentclass{sigplanconf}

@@

\usepackage{listings}
%\usepackage[scaled]{luximono}

%\usepackage{natbib}

% ----- begin macros

\lstdefinelanguage{Scala}%
{morekeywords={abstract,%
  case,catch,char,class,%
  def,else,extends,final,for,%
  if,import,implicit,%
  match,module,%
  new,null,%
  object,override,%
  package,private,protected,public,%
  for,public,return,super,%
  this,throw,trait,try,type,%
  val,var,%
  with,%
  yield,%
  lazy%
  },%
  sensitive,%
  morecomment=[l]//,%
  morecomment=[s]{/*}{*/},%
  morestring=[b]",%
  morestring=[b]',%
  showstringspaces=false%
}[keywords,comments,strings]%

\lstdefinelanguage{JavaScript}%
{morekeywords={for, var, attributes, class, classend, do, else, empty, endif, endwhile, fail, function,
functionend, if, implements, in, inherit, inout, not, of, operations, out, return,
then, types, while, use},%
  sensitive,%
  morecomment=[l]//,%
  morecomment=[s]{/*}{*/},%
  morestring=[b]",%
  morestring=[b]',%
  showstringspaces=false%
}[keywords,comments,strings]%

\lstset{language=Scala,%
  mathescape=false,%
%  columns=[c]fixed,%
  aboveskip=\smallskipamount,
  belowskip=\smallskipamount,
%  basewidth={0.5em, 0.4em},%
  basicstyle=\footnotesize,%
  captionpos=b,
  keywordstyle=\bfseries%\sffamily\bfseries,%
%  keywordstyle=\sffamily\bfseries,%
%  xleftmargin=0.5cm
}

\newcommand{\commentstyle}[1]{\slseries{#1}}
\newcommand{\keywordstyle}[1]{\bfseries{#1}}

\lstnewenvironment{slisting}{\lstset{language=Scala}}{}

\newcommand{\code}[1]{\lstinline[language=Scala,columns=fixed,basicstyle=\footnotesize]|#1|}

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist

@@

\conferenceinfo{GPCE~'13}{October 27--28, 2013, Indianapolis, Indiana, USA} 
\copyrightyear{2013} \copyrightdata{978-1-4503-2373-4/13/10} \doi{2517208.2517227}

@@

%\terms Languages, Software Engineering

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=7.5cm]{gpce19c-foy-langs.pdf}
\end{center}
\caption{Language engineering processes}
\vspace{-0.5cm}
\label{fig:langs}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=5cm]{gpce19c-foy-ir.pdf}
\end{center}
\caption{Intermediate representations returned by the evaluation of (a)
\code{document.find("\#add-user button")} and (b) \code{document.find("\#add-user")}}
\label{fig:ir}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=8cm]{gpce19c-foy-selectors-benchmark.png}
\caption{Micro-benchmark on the selectors abstraction}
\label{fig:selectors-benchmark}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=8cm]{gpce19c-foy-microbenchmark.png}
\caption{Micro-benchmark on the optional values abstraction}
\label{micro-benchmark}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=8cm]{gpce19c-foy-chooze.png}
\caption{Benchmarks on a real application}
\label{benchmark}
\end{figure}

@@

\bibliographystyle{abbrvnat}
\begin{thebibliography}{24}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi: #1}\else
  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

\bibitem[Ashkenas(2011)]{Ashkenas2011_CoffeeScript}
J.~Ashkenas.
\newblock Coffeescript, 2011.

\bibitem[Bibeault and Kats(2008)]{Bibeault08_jQuery}
B.~Bibeault and Y.~Kats.
\newblock \emph{jQuery in Action}.
\newblock Dreamtech Press, 2008.

\bibitem[Brown et~al.(2011)Brown, Sujeeth, Lee, Rompf, Chafi, Odersky, and
  Olukotun]{Brown11_Parallel}
K.~J. Brown, A.~K. Sujeeth, H.~J. Lee, T.~Rompf, H.~Chafi, M.~Odersky, and
  K.~Olukotun.
\newblock A heterogeneous parallel framework for domain-specific languages.
\newblock In \emph{Parallel Architectures and Compilation Techniques (PACT),
  2011 International Conference on}, pages 89--100. IEEE, 2011.

\bibitem[Cannasse(2008)]{Cannasse08_HaXe}
N.~Cannasse.
\newblock Using haxe.
\newblock \emph{The Essential Guide to Open Source Flash Development}, pages
  227--244, 2008.

\bibitem[Chaganti(2007)]{Chaganti07_GWT}
P.~Chaganti.
\newblock \emph{Google Web Toolkit: GWT Java Ajax Programming}.
\newblock Packt Pub Limited, 2007.

\bibitem[Cooper et~al.(2007)Cooper, Lindley, Wadler, and
  Yallop]{Cooper07_Links}
E.~Cooper, S.~Lindley, P.~Wadler, and J.~Yallop.
\newblock Links: Web programming without tiers.
\newblock In \emph{Formal Methods for Components and Objects}, pages 266--296.
  Springer, 2007.

\bibitem[Elliott et~al.(2003)Elliott, Finne, and
  De~Moor]{Elliott2003_Compiling}
C.~Elliott, S.~Finne, and O.~De~Moor.
\newblock Compiling embedded languages.
\newblock \emph{Journal of Functional Programming}, 13\penalty0 (3):\penalty0
  455--481, 2003.

\bibitem[Griffith(2011)]{Griffith11_Dart}
R.~Griffith.
\newblock The dart programming language for non-programmers-overview.
\newblock 2011.

\bibitem[Hoare(2009)]{Hoare09_Null}
T.~Hoare.
\newblock Null references: The billion dollar mistake.
\newblock \emph{Presentation at QCon London}, 2009.

\bibitem[Huang et~al.(2010)Huang, Xu, Tiwana, Mao, Zhang, and
  Bahl]{Huang10_Perf}
J.~Huang, Q.~Xu, B.~Tiwana, Z.~M. Mao, M.~Zhang, and P.~Bahl.
\newblock Anatomizing application performance differences on smartphones.
\newblock In \emph{Proceedings of the 8th international conference on Mobile
  systems, applications, and services}, pages 165--178. ACM, 2010.

\bibitem[Hudak(1996)]{Hudak96_DSEL}
P.~Hudak.
\newblock Building domain-specific embedded languages.
\newblock \emph{ACM Computing Surveys}, 28, 1996.
\newblock URL \url{http://dsel.ps}.

\bibitem[J{\o}rring and Scherlis(1986)]{Jorring1986_Staging}
U.~J{\o}rring and W.~L. Scherlis.
\newblock Compilers and staging transformations.
\newblock In \emph{Proceedings of the 13th ACM SIGACT-SIGPLAN symposium on
  Principles of programming languages}, pages 86--96. ACM, 1986.

\bibitem[Kossakowski et~al.(2012)Kossakowski, Amin, Rompf, and
  Odersky]{Kossakowski12_JsDESL}
G.~Kossakowski, N.~Amin, T.~Rompf, and M.~Odersky.
\newblock Java{S}cript as an {E}mbedded {DSL}.
\newblock In J.~Noble, editor, \emph{{ECOOP} 2012 -- {O}bject-{O}riented
  {P}rogramming}, volume 7313 of \emph{Lecture Notes in Computer Science},
  pages 409--434, Berlin, Heidelberg, 2012. Springer Berlin Heidelberg.
\newblock \doi{10.1007/978-3-642-31057-7_19}.
\newblock URL \url{https://github.com/js-scala/js-scala/}.

\bibitem[Kuuskeri and Mikkonen(2009)]{Kuuskeri09_PartitioningClientServer}
J.~Kuuskeri and T.~Mikkonen.
\newblock Partitioning web applications between the server and the client.
\newblock In \emph{Proceedings of the 2009 ACM symposium on Applied Computing},
  SAC '09, pages 647--652, New York, NY, USA, 2009. ACM.
\newblock ISBN 978-1-60558-166-8.
\newblock \doi{10.1145/1529282.1529416}.
\newblock URL \url{http://doi.acm.org/10.1145/1529282.1529416}.

\bibitem[McGranaghan(2011)]{McGranaghan11_ClojureScript}
M.~McGranaghan.
\newblock Clojurescript: Functional programming for javascript platforms.
\newblock \emph{Internet Computing, IEEE}, 15\penalty0 (6):\penalty0 97--102,
  2011.

\bibitem[Mikkonen and Taivalsaari(2008)]{Mikkonen08_SpaghettiJs}
T.~Mikkonen and A.~Taivalsaari.
\newblock Web applications - spaghetti code for the 21st century.
\newblock In \emph{Proceedings of the 2008 Sixth International Conference on
  Software Engineering Research, Management and Applications}, pages 319--328,
  Washington, DC, USA, 2008. IEEE Computer Society.
\newblock ISBN 978-0-7695-3302-5.
\newblock \doi{10.1109/SERA.2008.16}.
\newblock URL \url{http://dl.acm.org/citation.cfm?id=1443226.1444030}.

\bibitem[Nanda and Sinha(2009)]{Nanda09_Null}
M.~Nanda and S.~Sinha.
\newblock Accurate interprocedural null-dereference analysis for java.
\newblock In \emph{Software Engineering, 2009. ICSE 2009. IEEE 31st
  International Conference on}, pages 133--143. IEEE, 2009.

\bibitem[Preciado et~al.(2005)Preciado, Trigueros, S{\'a}nchez-Figueroa, and
  Comai]{Preciado05_RIAMethodologyNecessity}
J.~C. Preciado, M.~L. Trigueros, F.~S{\'a}nchez-Figueroa, and S.~Comai.
\newblock Necessity of methodologies to model rich internet applications.
\newblock In \emph{WSE}, pages 7--13. IEEE Computer Society, 2005.
\newblock ISBN 0-7695-2470-2.

\bibitem[Rodr{\'\i}guez-Echeverr{\'\i}a(2009)]{Echeverria09_RIA}
R.~Rodr{\'\i}guez-Echeverr{\'\i}a.
\newblock Ria: more than a nice face.
\newblock In \emph{Proceedings of the Doctolral Consortium of the International
  Conference on Web Engineering}, volume 484. CEUR-WS.org, 2009.

\bibitem[Rompf(2012)]{Rompf12_LMSThesis}
T.~Rompf.
\newblock \emph{Lightweight Modular Staging and Embedded Compilers: Abstraction
  without Regret for High-Level High-Performance Programming}.
\newblock PhD thesis, {\'E}COLE POLYTECHNIQUE F{\'E}D{\'E}RALE DE LAUSANNE,
  2012.

%\vfill\eject

\bibitem[Rompf et~al.(2012)Rompf, Sujeeth, Amin, Brown, Jovanovic, Lee,
  Jonnalagedda, Olukotun, and Odersky]{Rompf12_LMS}
T.~Rompf, A.~Sujeeth, N.~Amin, K.~Brown, V.~Jovanovic, H.~Lee, M.~Jonnalagedda,
  K.~Olukotun, and M.~Odersky.
\newblock Optimizing {D}ata {S}tructures in {H}igh-{L}evel {P}rograms: {N}ew
  {D}irections for {E}xtensible {C}ompilers based on {S}taging.
\newblock Technical report, 2012.

\bibitem[Souders(2008)]{Souders08_Perf}
S.~Souders.
\newblock High-performance web sites.
\newblock \emph{Communications of the ACM}, 51\penalty0 (12):\penalty0 36--41,
  2008.

\bibitem[Van~Deursen et~al.(2000)Van~Deursen, Klint, and Visser]{Van00_DSL}
A.~Van~Deursen, P.~Klint, and J.~Visser.
\newblock Domain-specific languages: an annotated bibliography.
\newblock \emph{ACM Sigplan Notices}, 35\penalty0 (6):\penalty0 26--36, 2000.

\bibitem[Visser(2007)]{Visser07}
E.~Visser.
\newblock {WebDSL}: {A} case study in domain-specific language engineering.
\newblock In R.~Lämmel, J.~Visser, and J.~Saraiva, editors, \emph{Generative
  and Transformational Techniques in Software Engineering II, International
  Summer School, {GTTSE} 2007}, volume 5235 of \emph{Lecture Notes in Computer
  Science}, pages 291--373, Braga, Portugal, 2007. Springer.
\newblock ISBN 978-3-540-88642-6.
\newblock \doi{http://dx.doi.org/10.1007/978-3-540-88643-3_7}.

\end{thebibliography}
%\begin{thebibliography}{}
%\softraggedright
%
%\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
%P. Q. Smith, and X. Y. Jones. ...reference text...
%
%\end{thebibliography}
%
\end{document}
